%-------------------------
% Resume in Latex Template
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textsl{\small#3} & \textsl{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, labelsep=0.75em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Jessica Liu} \\ \vspace{1pt}
    \small 
        (470) 380-3707 $|$
        \href{mailto:jessicatracyliu@gmail.com}{jessicatracyliu@gmail.com} $|$
        \href{https://www.linkedin.com/in/jessicaaliu/}{linkedin.com/in/jessicaaliu} $|$
        \href{https://jessicaliu06.github.io/portfolio}{jessicaliu06.github.io/portfolio}
\end{center}

%-----------EDUCATION-----------
\vspace{-0.75cm}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Aug. 2023 -- May 2027}
      {B.S. in Computer Science}{GPA: 4.00/4.00}
    \vspace{-1.15cm}
    \resumeSubheading
      {}{}
      {B.S. in Mathematics}{}

    \vspace{-0.5cm}
    \resumeSubheading
      {\small Relevant Coursework}{}
      {}{}
      \vspace{-0.7cm}
      \resumeItemListStart
        \resumeItem
            {\textsl{Computer Science:} Data Structures \& Algorithms, Design \& Analysis of Algorithms, Object-Oriented Design \& Analysis, Computer Architecture, Networking, Artificial Intelligence}
        \resumeItem
            {\textsl{Mathematics:} Linear Algebra, Combinatorics, Graph Theory, Probability Theory, Abstract Algebra, Differential Equations}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2025 -- Aug. 2025}
      {Niantic Spatial, Inc. $|$ Software Development Kit Team}{Bellevue, WA}
      \resumeItemListStart
        \resumeItem
            {Developed a visual positioning algorithm in Python to improve computer vision localization to large contiguous area maps with Wi-Fi fingerprinting, Wi-Fi topology analysis, and feature matching.}
        \resumeItem
            {Created an agentic AI application using Model Context Protocol to orchestrate augmented reality and geospatial tools to recommend real estate properties and answer detailed spatial queries about locations and interiors.}
      \resumeItemListEnd

    \vspace{-0.25cm}
    \resumeSubheading
      {Teaching Assistant}{Jan. 2024 -- Present}
      {Georgia Institute of Technology $|$ College of Computing}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem
            {\textbf{CS 3510 Design \& Analysis of Algorithms} (Fall 2025 -- Present): Teach advanced topics in algorithms (graph algorithms, dynamic programming, complexity theory); host office hours for classes of 600+ students.}
        \resumeItem
            {\textbf{CS 2110 Computer Organization \& Programming} (Spring 2025): Led weekly labs to teach fundamental concepts in computer architecture \& hardware, assembly programming, C programming, and memory management; hosted office hours for 800+ students.}
        \resumeItem
            {\textbf{CS 1331 Object-Oriented Programming} (Spring 2024 -- Fall 2024): Developed original teaching strategies, materials, and exercises for continued use in future semesters by 30+ TAs across 12 recitation sections attended by 800+ students; teach weekly recitations; host 6+ office hours per week.}
      \resumeItemListEnd

    \vspace{-0.25cm}
    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alpha Models, Inc.}{Alpharetta, GA}
      \resumeItemListStart
        \resumeItem{Developed an algorithmic C++ approach to the Traveling Salesman Problem to plan freight railroad maintenance.}
        \resumeItem{Implemented Java simulations to model railroad yard operations and optimize carrier labor and fuel expenses.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Breadboard Analyzer} $|$ \textsl{Python, OpenCV, Flask, React}}{}
          \resumeItemListStart
            \resumeItem{Built a web application to streamline debugging electronic circuit prototypes by generating schematic diagrams from photos of breadboards.}
            \resumeItem{Implemented image processing techniques using OpenCV for contour, grid, and edge detection to identify electronic components, including wires and integrated circuits.}
            \resumeItem{Developed a custom graph data structure to model circuits from computer vision data, and designed a modified depth-first search algorithm to convert data into Boolean logic expressions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


 %-----------LEADERSHIP & COMMUNITY INVOLVEMENT-----------
 \section{Leadership \& Community Involvement}
 \resumeSubHeadingListStart
     \resumeSubheading
    {Machine Shop Lead Instructor}{Aug. 2025 -- Present}
    {The Hive Interdisciplinary Makerspace -- Georgia Institute of Technology}{Atlanta, GA}
    \resumeItemListStart
        \resumeItem{Supervise and improve safety and efficiency of machine shop; train instructors and end users on wood- \& metal-working machinery; design instructional materials and project blueprints; lead workshops to develop woodworking skills.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{0.1cm}
 \begin{itemize}[leftmargin=*, label={}]
    \small\item 
    \begin{tabular*}{0.97\textwidth}[t]{l@{\hspace{0.25cm}}l}
      \textbf{Languages:} & \text{Java, C, C++, Python, C\#, SQL, Assembly, JavaScript, TypeScript, HTML/CSS} \\
      \textbf{Tools:} & \text{Git, Unity, MySQL, Firebase, MATLAB, Mathematica, Tableau, LaTeX, Android Studio, Docker, Linux,} \\
      & \text{Bash, GDB Debugger, CMake, Bazel, Jupyter Notebook} \\
      \textbf{Libraries:} & \text{Pandas, NumPy, Matplotlib, PyTorch, TensorFlow, OpenCV, Flask, MCP, JUnit}
    \end{tabular*} \vspace{-6pt}
 \end{itemize}
 
%-------------------------------------------
\end{document}